<h3><center> MATH2270 - Data Visualisation: Assignment 3</h3>
<h5> Visualisations to support the article - "Whatever happened to the 15-hour workweek?" - on the conversation website </h>
</center>
</br></br>

<h4>Student Details</h4>
* Saurabh Mallik (S3623575)
</br>
</br>

<h4>Introduction</h4>
The purpose of these visualisations, is to support the article "Whatever happened to the 15-hour workweek?", on the conversation website. The article can be view on the following link https://theconversation.com/whatever-happened-to-the-15-hour-workweek-84781.

There are three visualisations that have been created to support the article, the details of which are as follows.</br>
1. Time-series plots for the average hours worked by a full-time employee in a year from six countries, namely Australia, Denmark, Germany, Korea, United Kingdom and the United States. This time-series spans from 2001 to 2016.</br>
2. A bar chart of the average weekly hours worked by a full-time male and female in the same countries.</br>
3. Time-series plots for GDP per hour worked for these countries spanning from 2001 to 2016. This graph shows the significant level of growth in productivity across nations over the years.

Data for these visualisations have been sourced from the OECD website under an open license:</br>
- Annual & Weekly hours worked (https://stats.oecd.org/Index.aspx?DataSetCode=ANHRS)</br>
- GDP per hour worked (https://data.oecd.org/lprdty/gdp-per-hour-worked.htm)
</br>
</br>

<h4>Visualisations</h4>
```{r setup, include=FALSE}
library(devtools)
dev_mode(TRUE)
devtools::install_github("hadley/ggplot2")
devtools::install_github("ropensci/plotly")
library(flexdashboard)
library(ggplot2)
library(plotly)
library(readr)
library(dplyr)
```

Loading the Datasets
```{r}
annual <- read_csv("annual.csv")
ausavg <- read_csv("avg hrs week.csv")
gdp <- read_csv("DP_LIVE_17102017185245898.csv")
```

Visualisation #1 - Time-series plots for the average hours worked by a full-time employee in a year from six countries, namely Australia, Denmark, Germany, Korea, United Kingdom and the United States. This time-series spans from 2001 to 2016.

```{r}
updatemenus <- list(
  list(
    active = 0,
    x = -.125,
    type= 'buttons',
    buttons = list(
      list(
        label = "Australia",
        method = "update",
        args = list(list(visible = c(TRUE, "legendonly", "legendonly", 
                                     "legendonly", "legendonly","legendonly")))),
      list(
        label = "Denmark",
        method = "update",
        args = list(list(visible = c("legendonly", TRUE, "legendonly", 
                                     "legendonly", "legendonly", "legendonly")))),
      list(
        label = "Germany",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly", TRUE, 
                                     "legendonly", "legendonly","legendonly")))),
      
      list(
        label = "Korea",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly","legendonly", TRUE, 
                                     "legendonly", "legendonly")))),
      
      list(
        label = "United Kingdom",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly","legendonly","legendonly", TRUE, 
                                     "legendonly")))),
      
      list(
        label = "United States",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly", "legendonly","legendonly","legendonly",TRUE))))
      
    )
  )
)

p1 <- plot_ly(data = annual) %>% 
  
  add_lines(x=~Time, y=~Value, name = "Australia", visible = "legendonly") %>%
  add_lines(x=~Time6, y=~Value6, name = "Denmark", visible = "legendonly") %>%
  add_lines(x=~Time3, y=~Value3, name = "Germany", visible = "legendonly") %>%
  add_lines(x=~Time2, y=~Value2, name = "Korea", visible = "legendonly") %>%
  add_lines(x=~Time4, y=~Value4, name = "United Kingdom", visible = "legendonly") %>%
  add_lines(x=~Time5, y=~Value5, name = "United States", visible = "legendonly") %>%
        
  layout(title= "Time-series of average weekly hours worked by individuals (2001 to 2016)", showlegend=TRUE,
         xaxis=list(zeroline = FALSE,title="Year", rangeslider = list(type = "date")),
         yaxis=list(zeroline = FALSE,title="Weekly Hours"),
         updatemenus=updatemenus)

p1
```
<h6>Data sourced from https://stats.oecd.org/Index.aspx?DataSetCode=ANHRS</h6></br>


Visualisation #2 - A bar chart of the average weekly hours worked by a full-time male and female in the same countries.

```{r}
p2 <- plot_ly(ausavg, x = ~Country, y = ~Value, color = ~Sex,
               alpha = 1) %>% 
  
  add_trace(type = "bar") %>% 
  
  layout(title = "Average weekly hours worked based on gender in 2016",
         yaxis = list(title = "Average Weekly Hours"))

p2
```
<h6>Data sourced from https://stats.oecd.org/Index.aspx?DataSetCode=ANHRS</h6></br>


Visalisation #3 - Time-series plots for GDP per hour worked for these countries spanning from 2001 to 2016. This graph shows the significant level of growth in productivity across nations over the years.

```{r}
updatemenus <- list(
  list(
    active = 0,
    x = -.125,
    type= 'buttons',
    buttons = list(
      list(
        label = "Australia",
        method = "update",
        args = list(list(visible = c(TRUE, "legendonly", "legendonly", 
                                     "legendonly", "legendonly","legendonly")))),
      list(
        label = "Denmark",
        method = "update",
        args = list(list(visible = c("legendonly", TRUE, "legendonly", 
                                     "legendonly", "legendonly", "legendonly")))),
      list(
        label = "Germany",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly", TRUE, 
                                     "legendonly", "legendonly","legendonly")))),
      
      list(
        label = "Korea",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly","legendonly", TRUE, 
                                     "legendonly", "legendonly")))),
      
      list(
        label = "United Kingdom",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly","legendonly","legendonly", TRUE, 
                                     "legendonly")))),
      
      list(
        label = "United States",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly", "legendonly","legendonly","legendonly",TRUE))))
      
    )
  )
)

p3 <- plot_ly(data = gdp) %>% 
  
  add_lines(x=~tim, y=~val, name = "Australia", visible = "legendonly") %>%
  add_lines(x=~tim2, y=~val2, name = "Denmark", visible = "legendonly") %>%
  add_lines(x=~tim3, y=~val3, name = "Germany", visible = "legendonly") %>%
  add_lines(x=~tim4, y=~val4, name = "Korea", visible = "legendonly") %>%
  add_lines(x=~tim5, y=~val5, name = "United Kingdom", visible = "legendonly") %>%
  add_lines(x=~tim6, y=~val6, name = "United States", visible = "legendonly") %>%
        
  layout(title = "Time-series of GDP per hour worked in some countries (2001-2016)",
         showlegend=TRUE,
         xaxis=list(zeroline = FALSE,title="Year", rangeslider = list(type = "date")),
         yaxis=list(zeroline = FALSE,title="GDP per hour worked (USD)"),
         updatemenus=updatemenus)

p3
```
<h6>Data sourced from https://data.oecd.org/lprdty/gdp-per-hour-worked.htm</h6></br>


